Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-12-19 parts/sa.tex
minor comments of the reviewers

Finally, a bounce sequence on a sort $a$ (\pref{def:bs}) is a sequence of actions hitting $a$
in which the bounce process of each action is the hitter process of the following action.
Bounce sequences are used to find local solutions to a given objective:
\modMF{
indeed, the bounce sequences related to an objective $\PHobj{a_i}{a_j}$
only take depend on the bounces of the actions hitting the sort $a$.
}%
A bounce sequence on $a$ can be abstracted into the minimal sets of its hitters that are not in sort $a$ (\pref{def:aBS}).
This abstraction is later used to propagate an objective on a given sort
by creating new objectives on other sots.
In the following, we denote: $\Sol = \powerset(\PHproc)$.
\begin{definition}[Bounce sequence ($\BS$)]
\label{def:bs}
  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
  $\BS$ denotes the set of all bounce sequences, and
  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
  \[
    \BS(\PHobj{a_i}{a_j}) \DEF \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
  \]
  $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$
  and $\emptyseq \in \BS(\obj{a_i}{a_i})$
  \modMF{
  for a trivial objective $\PHobj{a_i}{a_i}$.
  }
\end{definition}
%
\begin{definition}[$\aBS:\Obj \rightarrow \powerset(\Sol)$]
\label{def:aBS}
  The \emph{abstractions of bounce sequences} of an objective $P$, denoted by the set $\aBS(P)$, are the sets of hitters of bounce sequences solving $P$:
  \[
    \aBS(P) \DEF \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
  \]
  \modMF{
  where $\forall P \in \Obj, \forall \zeta \in \BS(P)$:
  \[
    \abstr{\zeta} \DEF \{ \PHhitter(\zeta_n) \mid
    n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}
  \]
  }%
\end{definition}

@@

We denote $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
\pref{lem:uconcr-ctx} is used to over-approximate the initial context $\ctx$.

\begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
Given $\w\in\OS$, $\concr(\w)$ is the set of minimal scenarios concretising $\w$ in the
context $\ctx$. It is defined as the largest set satisfying the following conditions:
\begin{enumerate}[(i)]
\item $\forall\delta\in\concr(\w), \modMF{\delta\in\Sce(\ctx)}$
\item $\forall\delta\in\concr(\w),
  \exists \phi:\indexes{\w}\to\indexes{\delta},
    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m)),$
\\\hspace*{2cm}$\forall n\in\indexes{\w}, \PHbounce(\w_n) \in \ctx\play\delta_{1..\phi(n)}$
\item $\forall\delta,\delta'\in\concr(\w)
				\card{\delta}\leq\card{\delta'} \Rightarrow
					\delta\neq\delta'_{1..\card{\delta}}$.
\end{enumerate}
\end{definition}
\begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
\label{def:uconcr}
  \[
  \modMF{\forall \w \in \OS,}
  \uconcr(\w) \DEF
  \begin{cases}
    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \delta \in \Sce(s) \\
    \emptyset & \text{else.}
  \end{cases}
  \]
\end{definition}
% 
\begin{lemma}
\label{lem:uconcr-ctx}
  $\ctx \subseteq \ctx' \wedge \muconcr_{\ctx'}(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx}(\w) \neq \emptyset$.
\end{lemma}

For any objective $P$ and context $\ctx$, \pref{def:maxCont} gives the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$, given by $\gCont_\ctx(\PHsort(P), P)$.
\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
  \label{def:maxCont}
  \begin{align*}
    \gCont_\ctx(a,P) \DEF
    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
    \enspace.
  \end{align*}
\end{definition}

\modMF{
A graph of local causality $\aB = (\cwV, \cwE)$
is a graph where $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ is the set of vertices
and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges.
Such a graph aims a describing the requirements of a given reachability
problem, that is, the reachability of $\w$ from the initial context $\ctx$.
Thus, a node in $\PHproc$ represents a process required to play an action,
a node in $\Obj$ is an objective to reach a given process
and a node in $\Sol$ is a set of hitter processes required for the solving
of an objective.
}

@@

\modMF{
However, this graph $\aB$ alone is not sufficient to check the reachability of
an objective sequence $\w$ from an initial context $\ctx$;
indeed, the reachability of each intermediate required process
is only checked starting from the context $\ctx$,
although this context may be modified by other objectives.
Therefore, such a reachability requires the building of the
\emph{saturated graph of local causality} (\pref{def:glc})
which is obtained by iteratively saturating the initial context with all
processes referenced in the graph,
until reaching a fixed point.
Such a fixed point always exists because the size of the context
is limited by the size of the initial PH model.
The set of processes contained in a graph of local causality
is given by:
\begin{align*}
  \allprocs(\cwV, \cwE) = (\cwV \cap \Proc) &\cup \{ \PHtarget(P) \mid P \in \cwV \cap \Obj \}\\
  & \cup \{ P \neq \w \Rightarrow \PHbounce(P) \mid P \in \cwV \cap \Obj \}
\end{align*}
where, if the objective sequence $\w$ consists of only one element,
then we can omit the hitter of this objective
if it does not appear elsewhere in the graph.
}

\begin{definition}
\label{def:glc}
  The \modMF{saturated} graph of local causality $\cwB \DEF (\Bv, \Be)$ is defined as:
  $\cwB \DEF \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB \DEF (\cwV, \cwE)$ is the smallest graph with
  $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$
  so that:
  \begin{align}
    \w &\subseteq \cwV \label{eq:Vw} \\
%    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
    P \in \cwVObj \wedge ps \in \modMF{\aBS}(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
    ps \in \cwVSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
    a \in \components \wedge a_i \in \cwVProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
    a \in \cs \wedge a_i \in \cwVProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
    P \in \cwVObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
  \end{align}
\end{definition}

\todo{“Saturated” partout}

In the saturated graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$
is said to be coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the children processes of $ps$.
Then, \pref{th:approxinf} gives a sufficient condition for the concretisation of a sequence of objectives in a given context,
which is derived immediately from the saturated graph of local causality.
A proof of this theorem is given in \pref{suppl:demoapproxinf}.
\begin{definition}[Coherent edge]
\label{def:coherent}
  An edge $(x, y) \in \cwE$ is said to be coherent if and only if:
  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no children process $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_j$.
\end{definition}

@@

Computing the saturated graph of local causality is polynomial in the number of sorts in $\PH$ and exponential in the number of processes in one sort.
Checking the properties allowing to apply \pref{th:approxinf} is polynomial in the size of the graph.
Furthermore, it is possible to compute only a subset of $\V \cap \Sol$;
in this case, the overall method turns out to be exponential in the number of solutions to each objective.
Our method can thus be considered as efficient compared to regular model-checking which is usually PSPACE-complete~\cite{Harel02}.

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (a0)
    (b11) edge (b11s)
    ;
    \end{tikzpicture}
  \caption{
  \label{fig:sa-livelock}
    The saturated graph of local causality of the PH model in \pref{fig:ph-livelock}
    for the objective $\w = \PHobj{c_0}{c_1}$ and the initial context $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.
    Rectangular nodes containing a single process are elements in $\Proc$,
    borderless nodes containing a couple of processes are elements in $\Obj$
    and circle nodes are elements in $\Sol$.
    \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
    Indeed, $a_0 \in \Proc$ is a child of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
  }
\end{figure}
\end{example}

@@

It is also possible to compute the reachability of a set of states $S \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in S$,
or on a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subset \PHs$ by adapting the sort $\total$ with: $\PHl_\total = \PHsubl[\PHl]_S$

@@

From \pref{th:approxinf}, we can deduce that
for any scenario $\delta$ in $\uconcr(P)$,
there exists a set of processes $ps\in\lastprocs(P)$
such that $ps \subset (s\play\delta)$.
Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
with $\ctx'=\ctx\Cap\procs(\mycwB{\ctx}{P})$,
there exists a scenario $\delta'$ concretising $\w'$ from the
state $(s\play\delta)$.
Therefore, the scenario $\delta\concat\delta'$ concretises
$\w$.

\begin{definition}[$\lastprocs$]
\label{def:lastprocs}
Given an objective $\obj{a_i}{a_j}$, $\lastprocs:
\Obj\to\powerset(\powerset(\Proc))$ is
defined as the largest set such that, $\forall lps\in\lastprocs(\obj{a_i}{a_j})$, 
$lps\in\powerset(\Proc)$,
\begin{enumerate}
\item $a_j\in lps$;
\item $\exists\zeta\in\BS(\obj{a_i}{a_j}),
    \PHsort(\hitter{\zeta_{\card\zeta}}) \neq 
		\PHsort(\bounce{\zeta_{\card\zeta}})
		 \Rightarrow
		  \hitter{\zeta_{\card\zeta}}\in lps$;
\item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j), ps\subset lps$;
\item $\nexists lps'\in\lastprocs(\obj{a_i}{a_j}), lps'\subset lps \wedge
									lps'\neq lps$.
\end{enumerate}
\end{definition}

\begin{theorem}[Sequential under-approximation]
\label{thm:ordered-ua}
Given a Process Hitting $(\PHs; \PHl; \PHa^{\langle 2 \rangle})$
that satisfies \pref{cr:bounded} and \pref{cr:compcs},
a context $\ctx$ and an objective sequence $\w =
P\concat\w'\in\OS$,
$\uconcr(P)\neq\emptyset \wedge
	\forall ps \in\lastprocs(P),
	\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset
	\Longrightarrow \uconcr(\w)\neq\emptyset$,
where $\ctx' = \ctx\Cap\procs(\mycwB{\ctx}{P})$.
\end{theorem}
\begin{proof}
If $\uconcr(P)\neq\emptyset$,
for all $s\in \PHl, s\subset\ctx$,
there exists a scenario $\delta\in\uconcr(P)\cap\Sce(s)$;
from \pref{def:lastprocs} and proof of \pref{th:approxinf},
$\exists ps\in\lastprocs(P)$ such that
$(s\play\delta)\subset\ctx'\Cap ps$.
Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
there exists a scenario $\delta'\in\muconcr_{\ctx'\Cap ps}(\w')$ such that
$\delta'\in\Sce(s\play\delta)$.
Hence, $\delta\concat\delta'$ is a scenario playable in $s$.
Therefore, for all $s\in \PHl, s\subset\ctx$, there exists a scenario
concretising $\w$.
Hence, $\uconcr(\w)\neq\emptyset$.
\end{proof}

>>>>

Finally, a bounce sequence on a sort $a$ (\pref{def:bs}) is a sequence of actions hitting $a$
in which the bounce process of each action is the hitter process of the following action.
Bounce sequences are used to find local solutions to a given objective:
\modMF{
indeed, the bounce sequences related to an objective $\PHobj{a_i}{a_j}$
only take depend on the bounces of the actions hitting the sort $a$.
}%
A bounce sequence on $a$ can be abstracted into the minimal sets of its hitters that are not in sort $a$ (\pref{def:aBS}).
This abstraction is later used to propagate an objective on a given sort
by creating new objectives on other sorts.
In the following, we denote: $\Sol = \powerset(\PHproc)$.
\begin{definition}[Bounce sequence ($\BS$)]
\label{def:bs}
  A \emph{bounce sequence} $\zeta$ is a sequence of actions so that $\forall n \in \indexes{\zeta}, n < |\zeta|, \PHbounce(\zeta_{n}) = \PHtarget(\zeta_{n+1})$.
  $\BS$ denotes the set of all bounce sequences, and
  $\BS(P)$ denotes the set of bounce sequences \emph{solving} an objective $P$:
  \[
    \BS(\PHobj{a_i}{a_j}) \DEF \{ \zeta \in \BS \mid \PHtarget(\zeta_1)= a_i \wedge \PHbounce(\zeta_{|\zeta|}) = a_j \} \enspace.
  \]
  $\BS(\obj{a_i}{a_j}) = \emptyset$ if there is no way to reach $a_j$ from $a_i$
  and $\emptyseq \in \BS(\obj{a_i}{a_i})$
  \modMF{
  for a trivial objective $\PHobj{a_i}{a_i}$.
  }
\end{definition}
%
\begin{definition}[$\aBS:\Obj \rightarrow \powerset(\Sol)$]
\label{def:aBS}
  The \emph{abstractions of bounce sequences} of an objective $P$, denoted by the set $\aBS(P)$, are the sets of hitters of bounce sequences solving $P$:
  \[
    \aBS(P) \DEF \{ \abstr{\zeta} \in \Sol \mid \zeta \in \BS(P), \nexists \zeta' \in \BS(P), \abstr{\zeta'} \subsetneq \abstr{\zeta} \} \enspace,
  \]
  \modMF{
  where $\forall P \in \Obj, \forall \zeta \in \BS(P)$:
  \[
    \abstr{\zeta} \DEF \{ \PHhitter(\zeta_n) \mid
    n \in \indexes{\zeta} \wedge \PHsort(\PHhitter(\zeta_n)) \neq \PHsort(P) \}
  \]
  }%
\end{definition}

@@

We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence $\w$ in the context $\ctx$.
In \pref{def:uconcr}, we define $\uconcr(\w)$ as equal to $\concr(\w)$ if and only if $\concr(\w)$ contains scenarios starting from all states $s \subseteq \ctx$.
\pref{lem:uconcr-ctx} is used to over-approximate the initial context $\ctx$.

\begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
Given $\w\in\OS$, $\concr(\w)$ is the set of minimal scenarios concretising $\w$ in the
context $\ctx$. It is defined as the largest set satisfying the following conditions:
\begin{enumerate}[(i)]
\item $\forall\delta\in\concr(\w), \modMF{\delta\in\Sce(\ctx)}$
\item $\forall\delta\in\concr(\w),
  \exists \phi:\indexes{\w}\to\indexes{\delta},
    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m)),$
\\\hspace*{2cm}$\forall n\in\indexes{\w}, \PHbounce(\w_n) \in \ctx\play\delta_{1..\phi(n)}$
\item $\forall\delta,\delta'\in\concr(\w)
				\card{\delta}\leq\card{\delta'} \Rightarrow
					\delta\neq\delta'_{1..\card{\delta}}$.
\end{enumerate}
\end{definition}

\noindent
The notation $\delta_{a..b}$ denotes the subsequence of $\delta$
between indexes $a$ and $b$, as defined on page \pageref{notations}.

\begin{definition}[$\uconcr: \OS \rightarrow \powerset(\Sce)$]
\label{def:uconcr}
  \[
  \modMF{\forall \w \in \OS,}
  \uconcr(\w) \DEF
  \begin{cases}
    \concr(\w) & \text{if } \forall s \in \PHl, s \subseteq \ctx, \exists \delta \in \concr(\w), \delta \in \Sce(s) \\
    \emptyset & \text{else.}
  \end{cases}
  \]
\end{definition}
% 
\begin{lemma}
\label{lem:uconcr-ctx}
  $\ctx \subseteq \ctx' \wedge \muconcr_{\ctx'}(\w) \neq \emptyset \Longrightarrow \muconcr_{\ctx}(\w) \neq \emptyset$.
\end{lemma}

For any objective $P$ and context $\ctx$, \pref{def:maxCont} gives the set of processes of sort $\PHsort(P)$ that are required to solve $P$ in $\ctx$, denoted by $\gCont_\ctx(\PHsort(P), P)$.
\begin{definition}[$\gCont_\ctx : \Sigma \times \Obj \rightarrow \powerset(\PHproc)$]
  \label{def:maxCont}
  \begin{align*}
    \gCont_\ctx(a,P) \DEF
    \{ p \in \PHproc &\mid \exists ps \in \aBS(P), \exists b_i \in ps, b = a \wedge p = b_i \\
      & \vee b \neq a \wedge p \in \gCont_\ctx(a, \PHobj{b_j}{b_i}) \wedge b_j \in \PHget{\ctx}{b} \}
    \enspace.
  \end{align*}
\end{definition}

\modMF{
A graph of local causality $\myB = (\cwV, \cwE)$
is a graph where $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ is the set of vertices
and $\cwE \subseteq \cwV \times \cwV$ is the set of oriented edges.
Such a graph aims a describing the requirements of a given reachability
problem, that is, the reachability of $\w$ from the initial context $\ctx$.
Thus, a node in $\PHproc$ represents a process required to play an action,
a node in $\Obj$ is an objective to reach a given process
and a node in $\Sol$ is a set of hitter processes required for the solving
of an objective.
}

@@

\modMF{
However, this graph $\myB$ alone is not sufficient to check the reachability of
an objective sequence $\w$ from an initial context $\ctx$;
indeed, the reachability of each intermediate required process
is only checked starting from the context $\ctx$,
although this context may be modified by other objectives.
Therefore, such a reachability requires the building of the
\emph{saturated graph of local causality} (\pref{def:glc})
which is obtained by iteratively saturating the initial context with all
processes referenced in the graph,
until reaching a fixed point.
Such a fixed point always exists because the size of the context
is limited by the size of the initial PH model.
The set of processes contained in a graph of local causality
is given by:
\begin{align*}
  \allprocs(\cwV, \cwE) = (\cwV \cap \Proc) &\cup \{ \PHtarget(P) \mid P \in \cwV \cap \Obj \}\\
  & \cup \{ P \neq \w \Rightarrow \PHbounce(P) \mid P \in \cwV \cap \Obj \}
\end{align*}
where, if the objective sequence $\w$ consists of only one element,
then we can omit the hitter of this objective
if it does not appear elsewhere in the graph.
}

\begin{definition}
\label{def:glc}
  The \modMF{saturated} graph of local causality $\cwB \DEF (\Bv, \Be)$ is defined as:
  $\cwB \DEF \lfp{\aB^\w_\ctx}{\myB}{\aB^\w_{\ctx \Cap \allprocs(\myB)}}$,
  where $\myB \DEF (\cwV, \cwE)$ is the smallest graph with
  $\cwV \subseteq \Proc \cup \Obj \cup \Sol$ and $\cwE \subseteq \cwV \times \cwV$
  so that:
  \begin{align}
    \modMF{\toset{\w}} &\subseteq \cwV \label{eq:Vw} \\
%    P \in \cwVObj &\Rightarrow \PHbounce(P) \in \cwV \label{eq:Vproc} \\
    (x, y) \in \cwE &\Rightarrow y \in \cwV \label{eq:VE} \\
    P \in \cwVObj \wedge ps \in \modMF{\aBS}(P) &\Rightarrow (P, ps) \in \cwE \label{eq:ESol1} \\
    ps \in \cwVSol \wedge a_i \in ps &\Rightarrow (ps, a_i) \in \cwE \label{eq:ESol2} \\
    a \in \components \wedge a_i \in \cwVProc \wedge a_j \in \ctx &\Rightarrow (a_i, \PHobjp{a}{j}{i}) \in \cwE \label{eq:EReq} \\
    a \in \cs \wedge a_i \in \cwVProc \wedge ps \in \csState(a_i) &\Rightarrow (a_i, ps) \in \cwE \label{eq:EPrio} \\
    P \in \cwVObj \wedge q \in \gCont_\ctx(\PHsort(P), P) &\Rightarrow (P, \PHobj{q}{\PHbounce(P)}) \in \cwE \label{eq:ECont} \!
  \end{align}
\end{definition}

In the saturated graph of local causality, an edge $(p, ps) \in \Proc \times \Sol$
is said to be coherent (\pref{def:coherent}) if none of the processes in $ps$ conflict with the successor processes of $ps$,
\modMF{
that is, the successors of $ps$ that are in $\Bv \cap \Proc$.
}
Then, \pref{th:approxinf} gives a sufficient condition for the concretisation of a sequence of objectives in a given context,
which is derived immediately from the saturated graph of local causality.
A proof of this theorem is given in \pref{suppl:demoapproxinf}.
\begin{definition}[Coherent edge]
\label{def:coherent}
  An edge $(x, y) \in \cwE$ is said to be coherent if and only if:
  $(x, y) \in \Be \cap (\Proc \times \Sol) \Rightarrow y$ has no successor $a_j \in \Bv \cap \Proc$ so that $\exists a_i \in y$, $a_i \neq a_j$.
\end{definition}

@@

\modMF{
Regarding the complexity of the method,
computing the saturated graph of local causality is polynomial in the number of sorts in $\PH$ and exponential in the number of processes in one sort.
Checking the properties allowing to apply \pref{th:approxinf} is polynomial in the size of the graph.
Therefore, building and checking process can be considered polynomial in the size
of the PH model, provided that each sort only is contains a few processes.
We note that this is particularly true for biological models, where
each component usually contains a limited number of expression levels.
In addition, it is possible to “factorize” cooperative sorts
modelling more than two components,
as explained in \pref{ssec:cooperation},
in order to reduce their number of processes.
}

\modMF{
We note furthermore that in case the method developed in this section is not conclusive,
it is possible to compute only a subset of $\Bv \cap \Sol$,
by removing some solutions from the initial graph of local causality $\myB$,
or by removing them from the saturated graph of local causality $\cwB$ and by trimming it.
\pref{th:approxinf} is then still valid on the partial graph obtained,
which can lead to more conclusiveness by removing parts of the graph
that were not necessary for the reachability
(such as cycles for instance).
If one wants to test each possible subset of solutions,
the overall method then turns out to be exponential
in the number of solutions to each objective.
Our method can thus be considered as efficient compared to regular model-checking which is usually PSPACE-complete~\cite{Harel02}.
}

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (a0)
    (b11) edge (b11s)
    ;
    \end{tikzpicture}
  \caption{
  \label{fig:sa-livelock}
    The saturated graph of local causality of the PH model in \pref{fig:ph-livelock}
    for the objective $\w = \PHobj{c_0}{c_1}$ and the initial context $\ctx = \PHstate{a_1, b_0, c_0, ab_{10}}$.
    Rectangular nodes containing a single process are elements in $\Proc$,
    borderless nodes containing a couple of processes are elements in $\Obj$
    and circle nodes are elements in $\Sol$.
    \pref{th:approxinf} is inconclusive on this example as edge $(ab_{11}, \{ a_1, b_1 \}) \in \Proc \times \Sol$ (here represented with a double line) is not coherent (\pref{def:coherent}).
    Indeed, $a_0 \in \Proc$ is a successor of $\{ a_1, b_1 \}$, but $a_0 \neq a_1$ (and the same also stands for $b_0$).
  }
\end{figure}
\end{example}

@@

It is also possible to compute the reachability of a set of states $\Lambda \subseteq \PHl$ by creating several actions $\PHhit{\total_s}{\reach_0}{\reach_1}$ in $\PHh^{(2)}$ for each state $s \in \Lambda$,
or on a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subseteq \PHs$ by adapting the sort $\total$ with: $\PHl_\total = \PHsubl[\PHl]_S$

@@

From \pref{th:approxinf}, we can deduce that
for any scenario $\delta$ in $\uconcr(P)$,
there exists a set of processes $ps\in\lastprocs(P)$
such that $ps \subseteq (s\play\delta)$.
Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
with $\ctx'=\ctx\Cap\procs(\mycwB{\ctx}{P})$,
there exists a scenario $\delta'$ concretising $\w'$ from the
state $(s\play\delta)$.
Therefore, the scenario $\delta\concat\delta'$ concretises
$\w$.

\begin{definition}[$\lastprocs$]
\label{def:lastprocs}
Given an objective $\obj{a_i}{a_j}$, $\lastprocs:
\Obj\to\powerset(\powerset(\Proc))$ is
defined as the largest set such that, $\forall lps\in\lastprocs(\obj{a_i}{a_j})$, 
$lps\in\powerset(\Proc)$,
\begin{enumerate}
\item $a_j\in lps$;
\item $\exists\zeta\in\BS(\obj{a_i}{a_j}),
    \PHsort(\hitter{\zeta_{\card\zeta}}) \neq 
		\PHsort(\bounce{\zeta_{\card\zeta}})
		 \Rightarrow
		  \hitter{\zeta_{\card\zeta}}\in lps$;
\item $\forall b_j\in lps, b\in\cs, \exists ps\in\csState(b_j), ps\subseteq lps$;
\item $\nexists lps'\in\lastprocs(\obj{a_i}{a_j}), lps'\subset lps \wedge
									lps'\neq lps$.
\end{enumerate}
\end{definition}

\begin{theorem}[Sequential under-approximation]
\label{thm:ordered-ua}
Given a Process Hitting $(\PHs; \PHl; \PHa^{\langle 2 \rangle})$
that satisfies \pref{cr:bounded} and \pref{cr:compcs},
a context $\ctx$ and an objective sequence $\w =
P\concat\w'\in\OS$,
$\uconcr(P)\neq\emptyset \wedge
	\forall ps \in\lastprocs(P),
	\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset
	\Longrightarrow \uconcr(\w)\neq\emptyset$,
where $\ctx' = \ctx\Cap\procs(\mycwB{\ctx}{P})$.
\end{theorem}
\begin{proof}
If $\uconcr(P)\neq\emptyset$,
for all $s\in \PHl, s\subseteq\ctx$,
there exists a scenario $\delta\in\uconcr(P)\cap\Sce(s)$;
from \pref{def:lastprocs} and proof of \pref{th:approxinf},
$\exists ps\in\lastprocs(P)$ such that
$(s\play\delta)\subseteq\ctx'\Cap ps$.
Hence, if $\muconcr_{\ctx'\Cap ps}(\w')\neq\emptyset$,
there exists a scenario $\delta'\in\muconcr_{\ctx'\Cap ps}(\w')$ such that
$\delta'\in\Sce(s\play\delta)$.
Hence, $\delta\concat\delta'$ is a scenario playable in $s$.
Therefore, for all $s\in \PHl, s\subseteq\ctx$, there exists a scenario
concretising $\w$.
Hence, $\uconcr(\w)\neq\emptyset$.
\end{proof}
